### 2012-12-15 inst/examples/myer-example.Rmd
updated run shows differences in viability analysis, but GP still does optimally
Readme txt populated
Improved example of Allee model
* Compares to a Ricker estimated by MLE (#8)
* Considers fewer non-stationary observations, but include 0,0 as observation (#13)
* Includes scrap value (#10), though this does not guarentee no fishing under non-persistence estimation

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = TRUE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

```{r libraries, include=FALSE}
```

```{r graphing-options, include=FALSE}
```

@@

@@

@@

```{r gp-F-sim, dependson="gp-data"}
```

```{r par-F-sim}
```

```{r F-sim-plot}
```

@@

```{r echo=FALSE, results="as.is"}
bibliography("html")
```

>>>>

```{r set-options, echo = FALSE, cache = FALSE, external = TRUE}
opts_chunk$set(external = TRUE, cache = FALSE, cache.path = "myers-cache/")
read_chunk('gaussian-process-control.R')
library(knitcitations)
```

```{r libraries, include=FALSE}
```
```{r graphing-options, include=FALSE}
```

@@

We simulate data under this model, starting from a size of `r x_0_observed`.

@@

We consider the observations as ordered pairs of observations of current stock size $x_t$ and observed stock in the following year, $x_{t+1}$.  We add the pseudo-observation of $0,0$.  Alternatively we could condition strictly on solutions passing through the origin, though in practice the weaker assumption is often sufficient.

@@

```{r persistence-test}
```

```{r gp-F-sim, dependson=c("persistence-test", "gp-data")}
```

```{r par-F-sim, dependson="persistence-test"}
```

```{r F-sim-plot, dependson=c("gp-F-sim", "par-F-sim")}
```

@@

```{r echo=FALSE, results="asis"}
bibliography("html")
```
